The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-15 paper/ms.tex
hogg edits
no friends
white affiliations
actually we have c112

\author[0000-0002-6980-3392]{Timothy R. White}
\affiliation{Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia}

@@

\author{friends}
%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

@@

% describe halo algorithm
The `TV-min' halo method was first described by \citet{White2017} and applied to the Pleiades' Seven Sisters. It was also applied to Aldebaran with further developments by \citet{Farr2018}. We follow the Optimized-Weight Linear (OWL) photometry concept described by Hogg \&  Foreman-Mackey (2014, unpublished: preprint  \href{https://github.com/davidwhogg/OWL/}{\nolinkurl{github.com/davidwhogg/OWL/}}) in our assumptions. We assume that a star has a wide PSF sampled by many pixels with different sensitivities. This PSF varies at most to a small extent in time. The star moves around on the detector within a small region. We assume that our time series consists of many epochs sampled with a nearly even cadence. We do not have metadata describing the spacecraft motion, pixel gains, PSF variations or other noise processes. Because photometry is a linear operation, any estimator of the flux is necessarily a weighted sum of pixel values, which we choose to be time-invariant but note that this strong constraint is not necessary in general. In OWL and here, we search for a linear combination of pixels that is invariant with respect to the the noise processes but accurately preserved astrophysical signals.

The additional constraint beyond the OWL axioms is that some pixels are saturated, so that Simple Aperture Photometry (SAP) is inadvisable. Instead the measurements are made using the unsaturated pixels $p_j$ at the wings of the broad and structured PSF. We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux $f_i$ at epoch $i$ is

@@

% incorporation of k2sc
While the halo procedure produced a fairly clean light curve in most cases, there were nevertheless residual systematic errors related to spacecraft motion. In order to correct these, we employed the \textsc{k2sc} code \citep{Aigrain2015,k2sc}, which simultaneously models a light curve as a 3D Gaussian Process (GP) in time and predicted position (the K2 standard data product \textsc{pos\_corr}) in pixels $(x,y)$. The model prediction in time for fixed position is then a nonparametric model of the stellar variability, and the prediction for the $x,y$ component evaluated for fixed time represents the pointing systematics. We subtracted the systematics model from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science. Campaigns~9, 10, and~11 were observed in two blocks each, denoted C91/C92, C101/C102 and C111/C112 by the \ktwo Team. The target pixel files for C91, C92, and C101 include no position information, and there are no halo apertures for C112. As a result \textsc{k2sc}-corrected data are not available for these targets, and no halo light curves at all are available in C112.

@@

\begin{figure*}
\plotone{98_Tau_pub.pdf}
\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for the eclipsing binary 98~Tauri, in a similar format to Figure~\ref{fig:rholeo}. The residuals to the position and time GP are not shown, as the time GP fits poorly to the deep eclipse. The polynomial trend and Lomb-Scargle periodograms are conditioned on the out-of-transit points only.}
\label{fig:98tau}
\end{figure*}

>>>>

\author[0000-0002-6980-3392]{Timothy R. White}
\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
\affiliation{Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia}

@@

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

@@

% describe halo algorithm
The `TV-min' halo method was first described by \citet{White2017} and applied to the Pleiades' Seven Sisters. It was also applied to Aldebaran with further developments by \citet{Farr2018}. We follow the Optimized-Weight Linear (OWL) photometry concept described by Hogg \&  Foreman-Mackey (2014, unpublished: preprint  \href{https://github.com/davidwhogg/OWL/}{\nolinkurl{github.com/davidwhogg/OWL/}}) in our assumptions. We assume that a star has a wide PSF sampled by many pixels with different sensitivities. This PSF varies at most to a small extent in time. The star moves around on the detector within a small region. We assume that our time series consists of many epochs sampled with a nearly even cadence. We do not have metadata describing the spacecraft motion, pixel gains, PSF variations or other noise processes.

Because photometry is a linear operation, any estimator of the flux is necessarily a weighted sum of pixel values, which we choose to be time-invariant but note that this strong constraint is not necessary in general. In OWL and here, we search for a linear combination of pixels that is invariant with respect to the the noise processes but accurately preserved astrophysical signals.

The additional constraint beyond the OWL axioms is that some pixels are saturated, so that Simple Aperture Photometry (SAP) is inadvisable. Instead the measurements are made using the unsaturated pixels at the wings of the broad and structured PSF, with counts $p_ij$ where pixels are indexed by $j$ and epoch by $i$. We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux $f_i$ at epoch $i$ is a linear

@@

% incorporation of k2sc
While the halo procedure produced a fairly clean light curve in most cases, there were nevertheless residual systematic errors related to spacecraft motion. In order to correct these, we employed the \textsc{k2sc} code \citep{Aigrain2015,k2sc}, which simultaneously models a light curve as a 3D Gaussian Process (GP) in time and predicted position (the K2 standard data product \textsc{pos\_corr}) in pixels $(x,y)$. The model prediction in time for fixed position is then a nonparametric model of the stellar variability, and the prediction for the $x,y$ component evaluated for fixed time represents the pointing systematics. We subtracted the systematics model from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science. Campaigns~9, 10, and~11 were observed in two blocks each, denoted C91/C92, C101/C102 and C111/C112 by the \ktwo Team. The target pixel files for C91, C92, and C101 include no position information. As a result \textsc{k2sc}-corrected data are not available for these targets.

@@

\begin{figure*}
\plotone{98_Tau_pub.pdf}
\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for the eclipsing binary 98~Tauri, in a similar format to Figure~\ref{fig:rholeo}. The residuals to the position and time GP are not shown, as the time GP fits poorly to the deep eclipse, though this did not adversely affect the pointing systematics model. The polynomial trend and Lomb-Scargle periodograms are conditioned on the out-of-transit points only.}
\label{fig:98tau}
\end{figure*}
